Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2023-12-20 incidence-prevalence.tex
Fix notation

This section showed that, when using a prevalence survey such as CIS, the likelihood $p(\vec{x} \mid \vec{Z})$ is very well approximated by $\prob(\vec{X} = \vec{x} \mid \vec{P} = \E(\vec{P} \mid \vec{Z}))$.

>>>>

This section showed that, when using a prevalence survey such as CIS, the likelihood $p(\vec{x} \mid \vec{z})$ is very well approximated by $p(\vec{x} \mid \vec{P} = \E(\vec{P} \mid \vec{z}))$.
